\begin{abstract}
This study investigates the implementation and efficacy of DeputyDev, an AI-powered code review assistant developed to address inefficiencies in the software development process. The process of code review is highly inefficient for several reasons like it being a time consuming process, inconsistent feedback and review quality not being at par most of the time. Using our telemetry data we observed that at TATA 1mg, pull request (PR) processing exhibits significant inefficiencies, with average pick-up and review times of 73 and 82 hours respectively, resulting in a 6.2 days closure cycle. These delays negatively impact developer productivity and wellbeing, with context switching during reviews causing substantial time losses. Research from the University of California, Irvine indicates that interruptions can lead to an average of 23 minutes of lost focus  \cite{10.1145/1357054.1357072}, critically affecting code quality and timely delivery.

To address these challenges, we developed DeputyDev's PR review capabilities by providing automated, contextual code reviews. We conducted a rigorous double-controlled A/B experiment involving over 200 engineers to evaluate DeputyDev's impact on review times. The results demonstrated a statistically significant reduction in both per-PR and per-line-of-code review durations. After implementing safeguards to exclude outliers, DeputyDev has been effectively rolled out across the entire organization. Additionally, it has been made available to external companies as a Software-as-a-Service (SaaS) solution, currently supporting the daily work of numerous engineering professionals.

This study explores the implementation and effectiveness of AI-assisted code reviews in improving development workflow timelines and code quality while potentially reducing associated costs.
\end{abstract}