\section{Hypothesis}
We propose a two-stage code review process that integrates a DeputyDev with human expertise. This approach is hypothesized to enhance the efficiency and effectiveness of the overall code review process. The primary mechanisms through which this improvement is expected to occur are:

\begin{enumerate}
    \item \textbf{Reduction of cognitive load on human reviewers}: By employing DeputyDev as a first-level reviewer, we anticipate a significant decrease in the mental effort required from human reviewers. The AI system is expected to handle routine checks and common issues, allowing human reviewers to focus their cognitive resources on more complex, nuanced aspects of the code.
    
    \item \textbf{Minimization of context switching for code authors}: The immediate feedback provided by DeputyDev is hypothesized to reduce the frequency and duration of context switches for code authors. Instead of waiting for human reviewers to provide feedback on routine issues, authors can receive instant guidance on common errors and style violations, allowing them to make necessary adjustments promptly and maintain their coding flow.
    
    \item \textbf{Improved code quality}: The combination of AI and human expertise is expected to result in more thorough and comprehensive code reviews. DeputyDev can consistently check for a wide range of potential issues, while human reviewers can apply their experience and judgment to more subtle or context-dependent aspects of the code.
\end{enumerate}